Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-14 2016-Weak-FH-Bisim/WeakBisim.tex
Deux dessins en ATG

Finaly, we list here, in raw format, the 12 OTs computed by the tool:

@@

>>>>

Finaly, we list here, in raw format, the 12 OTs computed by the tool
\TODO{BUG! We should have 19 OTs...}:

@@

And here is a  drawing of this open automaton, slightly simplified for readability:

\begin{figure}[h]
  \centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
  \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
\end{figure}

And a partially saturated Automaton:

\begin{figure}[h]
  \centerline{\includegraphics[width=13cm]{ATG/SPImplWeakOpen}}
  \caption{Weak Open Automaton, partial}  \label{SimpleProtCounter:ImplWOA}
\end{figure}
